---
title: "Current experiments"
# author: "Thomas Van Hoey"
output: 
  html_document:
    theme: readable
    highlight: tango
    number_sections: true
    # css: ["./layout/ntu.css", "./layout/ntu-fonts.css"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(klippy)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy()
```


*Hi, welcome to the landing page of current studies.*
<br>
*If you are willing to participate, please select the relevant experiment shown below.*
<br>
*Thank you so much!*
<br>
*Dr. Thomas Van Hoey*
<br>
*HKU Linguistics*




# Familiary rating of ABB items

Date: 2021-11-16

Requirements:

* Be a native speaker of Mandarin Chinese

If you want to participate in this ABB experiment, please select the character set you are most familiar with.


## Simplified Chinese 简体版本

[Click here for the Simplified Chinese experiment](https://hku.au1.qualtrics.com/jfe/form/SV_77HB9Vswwx7LPD0)

Or copy the link to send it to all your friends: 

```{r, eval = FALSE}
https://hku.au1.qualtrics.com/jfe/form/SV_77HB9Vswwx7LPD0
```

## Traditional Chinese 繁體版本

[Click here for the Traditional Chinese experiment](https://hku.au1.qualtrics.com/jfe/form/SV_eL5OKy6ITdFNHds)

Or copy the link to send it to all your friends: 

```{r, eval = FALSE}
https://hku.au1.qualtrics.com/jfe/form/SV_eL5OKy6ITdFNHds
```












